\chapter*{Introduction}
\vspace{-1.25cm}
\section*{Message From The Author}
Hello all. Welcome to your journey through pre-calculus, the foundation for a branch of mathematics that will prove essential to various professions/fields (physics, business, economics, engineering, etc.) Not only that, understanding the depths of calculus (and pre-calculus) will change your perspective on mathematics. I truly hope you'll appreciate the wealth pre-calculus has to offer and enjoy the process of making it your own.

\subsection*{A Little About Me}
At the time of writing this text (March 2026), I'm a first-year community college student taking Multi-variable/Vector Calculus (Calc III). In the grand scheme of things, I'm not much further ahead in mathematics than you (if you're a student). But I thoroughly enjoy mathematics and want to show you the ins and outs of it. I hope I'm able to help you with your studies through my insights and explanations of concepts taught in pre-calculus.

\section*{Disclaimer}
Before continuing with the material, I'd like to make a few things completely clear:
\begin{enumerate}
    \item \textbf{This text is not a substitute for classroom instruction or your teacher/professor.} Your teachers and professors remain your \textbf{number one resource}. This text is intended only as a complimentary tool or additional material.
    \item \textbf{I am not an expert and have no formal qualifications} (i.e., degrees or certificates) beyond a high school diploma. Although I will do my best to explain the concepts of pre-calculus, this is another important reason why you should not rely solely on this text.
\end{enumerate}